---
output:
  html_document:
    fig_height: 8
    fig_width: 11
  pdf_document: default
---
# Universal Scalability Law tests
```{r echo=FALSE, message=FALSE}

source("ReportLib.R")

defaultFilePath <- "/Users/tim/workspace/account-modelling/ing-codegen-akka/results/2018-11-30T11:23:34.129+01:00-2PCvsCDACClosedContention1000FindMax"

option_list <- list(
  # make_option(c("-dir", "--from-directory"), action="store_true", default=FALSE,
  
    # help="Count the line numbers [default]"),
  make_option(c("-f", "--file"), default=defaultFilePath,
    help="File to process")
)

parser <- OptionParser(usage="%prog [options] file", option_list=option_list)

args <- parse_args(parser, positional_arguments = 0)
opt <- args$options
resultDir <- args$options$file
resultDir
```

```{r echo=FALSE, error=TRUE}

# if(resultDir != defaultFilePath) {
  # now we are run with proper command line arguments, so we really look what the input is
  variantDirNames <- list.dirs(resultDir, recursive=FALSE)
# }
# print(batchDirNames)

variantDirNames <- variantDirNames[!endsWith(variantDirNames,"CompareVariants_files")]

batchConf <- fromJSON(readLines(sprintf("%s/batch.conf", resultDir), warn=FALSE))
nName <- names(batchConf$n)

if (length(nName) != 1) stop(paste0("ERROR more values for n found: ", nName))

variants <- lapply(variantDirNames, function(variantDir) {
  # batchDir <- sprintf("%s/%s", resultDir, batch)
  experimentsDirNames <- list.dirs(variantDir, recursive=FALSE)

  print(variantDir)
  print(experimentsDirNames)

  variantJsonFileName <- sprintf("%s/variant.json", variantDir)
  print(variantJsonFileName)
  variantJson <- fromJSON(readLines(variantJsonFileName, warn=FALSE))
  print(variantJson$description)

  experiments <- lapply(experimentsDirNames, safeLoadExperiment)
  experiments <- Filter(Negate(is.null), experiments)

  list(
    title = last(unlist(strsplit(variantDir, "/"))), # could be from json file as well
    experiments = experiments,
    variant = variantJson
  )
})

variants <- Filter(Negate(is.null), variants)

```

## Scalability Plots

```{r error=TRUE}

variantBenchmarks <- lapply(variants, function(variant) {
  # print(experiments)
  
  print(toJSON(variant$variant, pretty = T))
  # print(nName)
  
  results <- sapply(variant$experiments, extractNodeCountVsThroughput, nName=nName)
  
  # print(results)
  # t(results)
  
  benchmarkDF <- as.data.frame(t(results))
  if(!length(benchmarkDF) == 0) {
    # print(benchmarkDF)
    benchmarkOrdered <- benchmarkDF[order(benchmarkDF$n), , ]
    # benchmark <- benchmarkOrdered[1:6, ]
    # benchmarkRest <- benchmarkOrdered[7:100, ]
    benchmark <- benchmarkOrdered
    # speedup
    # throughput(n) / througput(1)
    tp1 <- benchmark[benchmark$n == 1, "throughput"]
    if(length(tp1) == 0) {
       first <- benchmark[1,] # because ordered
       tp1 <- first$throughput / first$n
    }
    # print(tp1)
    benchmark$speedup <- benchmark$throughput / tp1
    benchmark$efficiency <- benchmark$throughput /benchmark$n / tp1
    
    # print(benchmark$speedup)
    
    # plot(benchmark)
    list(
      title = variant$title,
      benchmark = benchmark,
      tp1 = tp1
    )
  }
})

saveRDS(variantBenchmarks, paste0(resultDir, "/variantBenchmarks.rds"))


p <- plot_ly(type = 'scatter', mode = 'markers+lines')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'Throughput'), hovermode = 'compare'
           # ,legend = list(xanchor="center",yanchor="top",x = 0, y = -0.3)
           )

speedup <- plot_ly(type = 'scatter', mode = 'markers+lines')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'Speedup'), hovermode = 'compare'
           # ,legend = list(xanchor="center",yanchor="top",x = 0, y = -0.3)
           )

efficiency <- plot_ly(type = 'scatter', mode = 'markers+lines')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'Efficiency'), hovermode = 'compare'
           # ,legend = list(xanchor="center",yanchor="top",x = 0, y = -0.3)
           )

db <- plot_ly(type = 'scatter', mode = 'markers+lines')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'cpu usage'), hovermode = 'compare'
           # , legend = list(xanchor="center",yanchor="top",x = 0, y = -0.3)
           )

for(bb in variantBenchmarks) {
  # print(bb)
  # print(bb$benchmark)
  p <- add_trace(p, x=bb$benchmark$n, y=bb$benchmark$throughput, name=bb$title, 
                 # color = -bb$benchmark$percentiles99, colors="RdYlGn",
                 error_y = list(type = "data", array = bb$benchmark$throughput.max, arrayminus = bb$benchmark$throughput.min, symmetric = FALSE),
                 text = paste('p99: ', bb$benchmark$percentiles99, '\n users: ', bb$benchmark$users))
  if (any(bb$benchmark$failures > 0)) {
     print(paste0("FAILURES IN ", bb$title))
     p <- add_trace(p, x=bb$benchmark$n, y=bb$benchmark$failures, name=paste0(bb$title,'-failures'),
                    error_y = list(type = "data", array = bb$benchmark$failures.max, arrayminus = bb$benchmark$failures.min, symmetric = FALSE)
     )
                    # error_y = ~list(value = bb$benchmark$failures.sd)) 
  }
  
  speedup <- speedup %>%
    add_trace(bb$benchmark, x=bb$benchmark$n, y=bb$benchmark$speedup, name=bb$title) #, 
                 # color = -bb$benchmark$percentiles99, colors="RdYlGn", 
                 # error_y = list(type = "data", array = bb$benchmark$throughput.max, arrayminus = bb$benchmark$throughput.min, symmetric = FALSE))
  
  efficiency <- efficiency %>%
    add_trace(bb$benchmark, x=bb$benchmark$n, y=bb$benchmark$efficiency, name=bb$title)
  
  #cassandra
  db <- db %>%
    add_trace(x=bb$benchmark$n, y=bb$benchmark$dbCpu*100, name=paste0("dbcpu-", bb$title),
      error_y = list(type = "data", array = bb$benchmark$dbCpu.max, arrayminus = bb$benchmark$dbCpu.min, symmetric = FALSE), marker=list(symbol="cross")) %>%
    add_trace(x=bb$benchmark$n, y=bb$benchmark$cpu, name=paste0("cpu-", bb$title),
      error_y = list(type = "data", array = bb$benchmark$cpu.max, arrayminus = bb$benchmark$cpu.min, symmetric = FALSE))
}

maxSpeedup <- max(batchConf$n$`cluster-sizes`)

speedup <- speedup %>%
    add_lines(x=0:maxSpeedup, 0:maxSpeedup, name="Linear speedup", line = list(dash="dash"))

efficiency <- efficiency %>%
    add_lines(x=0:maxSpeedup, 1, name="Linear efficiency", line = list(dash="dash"))

p

```

### Relative Speedup

\[X(n) / X(1)\]

```{r error=TRUE, echo=FALSE}
speedup
```

### Efficiency

\[X(n) / n / X(1)\]

```{r error=TRUE, echo=FALSE}
efficiency
```


### Pirateplots per variant
```{r error=TRUE}

# system.time(
variantBeans <- lapply(variants, function(variant) {
  # print(experiments)
  
  # print(toJSON(variant$variant, pretty = T))
  
  results <- lapply(variant$experiments, function(exp) {
    gatling <- gatlingTotals(exp)$allTotal

    n <- getN(nName, exp$testDescription)
    gatling$n <- rep(n,nrow(gatling)) 
    
    #CPU
    # dbCpu <- exp$dbDuringExp$os.processCpuLoad
    # nodeCpu <- 1 - (exp$kamonTimersDuringExp[metric=='cpu-idle']$mean / 100)
    
    # print(gatling)
    gatling
  })
  
  combined <- rbindlist(results)
  combined[,variant:=variant$title]
  # ^  user  system elapsed 
  #    0.281   0.081   0.397 
  # combined$variant <- rep(variant$title,nrow(combined))
  # ^  user  system elapsed 
  #    0.378   0.044   0.501 
  combined
})
# )

# print(variantBeans)

for(variantBeanPlot in variantBeans) {
  variantName = variantBeanPlot$variant[[1]]
  
  # myFun = function(x) { x * 5000 }
  # 
  # pirateplot(count ~ n , data=variantBeanPlot, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)
  # curve(myFun, n = variantBeanPlot$n)
  # 
  # print(variantBeanPlot, class = TRUE)
  # 
  # g2 <- ggplot(variantBeanPlot, aes(n, count)) +
  #   # xlab("N") +
  #   # ylab("X(N)") +
  #   stat_function(fun=myFun, aes(colour="Linear")) +
  #    # geom_ribbon(aes(ymin = func2, ymax = func1), fill = "blue", alpha = .5) +
  #   # stat_function(fun=nearLinear, aes(colour="Near-linear")) +
  #   # stat_function(fun=nonLinear, aes(colour="Non-linear")) +
  #   # stat_function(fun=horizontal, aes(colour="Horizontal")) +
  #   geom_pirate(aes(colour = n, fill = n),
  #   points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1)) +
  #   theme(legend.position="bottom") + labs(color='variant')
  # # 
  # print(g2)
  
  # Hack to deal with int
  variantBeanPlot$n <- as.factor(variantBeanPlot$n)
  print(ggplot(variantBeanPlot, aes(x = n, y = count)) + 
    geom_pirate(aes(colour = n, fill = n),
                points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1)) +
    ggtitle(paste0(head(variantBeanPlot$variant), " total count")))
  print(ggplot(variantBeanPlot, aes(x = n, y = ok)) + 
    geom_pirate(aes(colour = n, fill = n),
                points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1)) +
    ggtitle(paste0(head(variantBeanPlot$variant), " total OK")))
}

all <- rbindlist(variantBeans)

# pirateplot(count ~ variant , data=all, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)

# pirateplot(ok ~ variant , data=all, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)

all$n <- as.factor(all$n)
all$variant <- as.factor(all$variant)

saveRDS(all, paste0(resultDir, "/all.pirate.rds"))
```

### Pirateplots combined

#### Total count
```{r error=TRUE}
ggplot(all, aes(x = variant, y = count)) + facet_wrap(~n) + 
  geom_pirate(aes(colour = variant, fill = variant),
              points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1), violins_params = list(scale = "width"))

ggplot(all, aes(x = n, y = count)) + facet_wrap(~variant) + 
  geom_pirate(aes(colour = n, fill = n),
              points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1), violins_params = list(scale = "width", width=0.5))
```

#### Only OKs

```{r error=TRUE}
ggplot(all, aes(x = variant, y = ok)) + facet_wrap(~n) + 
  geom_pirate(aes(colour = variant, fill = variant),
              points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1), violins_params = list(scale = "width"))

ggplot(all, aes(x = n, y = ok)) + facet_wrap(~variant) + 
  geom_pirate(aes(colour = n, fill = n),
              points_params = list(alpha = .03), lines_params = list(size = 0.2, alpha = 0.1), violins_params = list(scale = "width", width=0.5))
```

### Pirateplots per variant, in single plot
```{r error=TRUE}
ggplot(all, aes(x = n, y = count)) +
  geom_pirate(aes(colour = variant, fill = variant), points_params = list(alpha = .1), lines_params = list(size = 0.2, alpha = 0.1), 
              violins_params = list(scale = "width"),
              show.legend = TRUE) + 
  theme(legend.position="bottom") + labs(color='variant') + ggtitle("Total count vs n")

ggplot(all, aes(x = n, y = ok)) +
  geom_pirate(aes(colour = variant, fill = variant), points_params = list(alpha = .1), lines_params = list(size = 0.2, alpha = 0.1), 
              violins_params = list(scale = "width"),
              show.legend = TRUE) + 
  theme(legend.position="bottom") + labs(color='variant') + ggtitle("OK count vs n")
```

## Cassandra + App cpu load

```{r error=T}

db %>% layout(yaxis = list(
  # tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  range = c(0,100)
))

```

## DB Cpu usage
```{r error=T}

for(variant in variants) {
    dbCpus <- lapply(variant$experiments, function(exp) {
      
      dbCpuDF <- exp$dbDuringExp
      n <- getN(nName, exp$testDescription)
      dbCpuDF$heapMemoryUsage.used <- as.integer64(dbCpuDF$heapMemoryUsage.used) # hack to circumvent bug with int64 in rbindlist (https://github.com/Rdatatable/data.table/issues/1349)
      dbCpuDF$n <- n
    
      dbCpuDF
    })
    
    # print(dbCpus)
    
    dbCpusCombined <- rbindlist(dbCpus)
      
    tryCatch(pirateplot(os.processCpuLoad ~ n , data=dbCpusCombined, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, ylim = c(0,1), main = variant$title)
    , error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})
}

```

## App Cpu usage
```{r error=T}

for(variant in variants) {
    
    cpus <- lapply(variant$experiments, function(exp) {
      nodeCpuDF <- getMetricsData(exp, "host.cpu")[mode=='combined']
        
        
        # exp$kamonTimersDuringExp[metric=='cpu-idle']
      # nodeCpuDF$nodeCpu <- 1 - (nodeCpuDF$mean / 100)
      n <- getN(nName, exp$testDescription)
      nodeCpuDF$n <- n
    
      nodeCpuDF
    })
    
    # print(cpus)
    
    cpusCombined <- rbindlist(cpus)
      
    tryCatch(pirateplot(`p99.9` ~ n , data=cpusCombined, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, ylim = c(0,100), main = variant$title)
    , error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})
}

```

## 99p latency
```{r error=TRUE}
p <- plot_ly(type = 'scatter', mode = 'markers+lines')  %>%
    layout(xaxis= list(title='Count'), yaxis = list(title = 'p99'), hovermode = 'compare', legend = list(xanchor="center",yanchor="top",x = 0, y = -0.3))

for(bb in variantBenchmarks) {
  # print(bb)
  p <- add_trace(p, x=bb$benchmark$n, y=bb$benchmark$percentiles99, name=bb$title,
                 # color = -bb$benchmark$percentiles99, colors="RdYlGn", 
                 # error_y = list(type = "data", array = bb$benchmark$throughput.max, arrayminus = bb$benchmark$throughput.min, symmetric = FALSE),
                 size = bb$benchmark$throughput,
                 line = list(width = 2),
                 text = paste('throughput: ', bb$benchmark$throughput, 
                              '\n users: ', bb$benchmark$users,
                              '\n p99.9: ', bb$benchmark$`percentiles99-9`,
                              '\n p99: ', bb$benchmark$percentiles99,
                              '\n p95: ', bb$benchmark$percentiles95,
                              '\n p50: ', bb$benchmark$percentiles50
                              )
                 )
  # if (any(bb$benchmark$failures > 0)) {
     # print(paste0("FAILURES IN ", bb$title))
     # p <- add_trace(p, x=bb$benchmark$nodeCount, y=bb$benchmark$failures, name=paste0(bb$title,'-failures'), error_y = ~list(value = bb$benchmark$failures.sd)) 
  # }
}
p
```

## USL Fit

```{r error=TRUE}

p <- plot_ly(type = 'scatter', mode = 'markers')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'Throughput'))

maximum <- 0

usl.result <- list()

for(bb in variantBenchmarks) {
  print(bb$title)
  usl.model <- tryCatch({usl(throughput ~ n, bb$benchmark, method="default")},
    error=function(e){
      cat("ERROR :",conditionMessage(e), "\n")
      tryCatch({usl(throughput ~ n, bb$benchmark, method="nls")},
    error=function(e){
      cat("ERROR :",conditionMessage(e), "\n")
      usl(throughput ~ n, bb$benchmark, method="nlxb")})
    })
  
  if(inherits(usl.model, "error")) next
  
  summary <- summary(usl.model)$coefficients
  print(summary)
  usl.result[[ bb$title ]] <- usl.model
  # TODO make sure this is added to variantBenchmarks
  # bb$benchmark$usl.kappa = summary$kappa
  
  s <- scalability(usl.model)
  
  # linear <- function(N) { N * s(1) }
  # only works when n=1 is in the set
  # s1 <- bb$tp1
  # if(length(s1) == 0) {
  #   s1 <- s(1)
  # }
  # linear <- function(N) { N * s1 }
  linear2 <- scalability(usl.model,0,0)
  
  maxX = max(bb$benchmark$n) * 3

  p <- add_trace(p, x=bb$benchmark$n, y=bb$benchmark$throughput, name=bb$title) %>% #, name=t$hostname)
     # add_trace(p, x=bb$benchmark$n, y=bb$benchmark$failures) %>%
     add_lines(x = 0:maxX, y = s(0:maxX), name=paste0(bb$title, " USL")) %>% 
     # add_lines(x = 0:maxX, y = linear(0:maxX), line = list(dash="dash"), name=paste0(bb$title, " linear"))  %>% 
     add_lines(x = 0:maxX, y = linear2(0:maxX), line = list(dash="dash"), name=paste0(bb$title, " linear"))
  maximum <- max(max(max(bb$benchmark$throughput), s(0:maxX))*1.1, maximum)
}

for (i in seq_along(usl.result)) {
  name = names(usl.result)[[i]]
  usl.model <- usl.result[[i]]
  result = coef(usl.model)
  print(name)
  print(result)
  print(paste("peak.scalability ", peak.scalability(usl.model)))
  print(paste("scale.factor ", usl.model$scale.factor))
  NULL
}
# saveRDS(usl.result, paste0(resultDir, "/usl.result.rds"))

p %>% layout(yaxis = list(range = c(0, maximum))) 
```

### USL with all tps

```{r error=TRUE}

p <- plot_ly(type = 'scatter', mode = 'markers')  %>%
    layout(xaxis= list(title=nName), yaxis = list(title = 'Throughput (tps)'))

maximum <- 0

usl.result.tps <- list()

for(variantBeanPlot in variantBeans) {
  variantName = variantBeanPlot$variant[[1]]
  print(variantName)
  
  ori <- variantBeanPlot
  # variantBeanPlot <- variantBeanPlot[n < 13,]
  
  usl.model <- tryCatch({usl(ok ~ n, variantBeanPlot, method="default")},
    error=function(e){
      cat("ERROR :",conditionMessage(e), "\n")
      tryCatch({usl(ok ~ n, variantBeanPlot, method="nls")},
    error=function(e){
      cat("ERROR :",conditionMessage(e), "\n")
      tryCatch(usl(ok ~ n, variantBeanPlot, method="nlxb"), error=function(e){
         cat("ERROR :",conditionMessage(e), "\n")
         NULL
      })
    })
  })
  
  if(is.null(usl.model) || inherits(usl.model, "error")) {
    cat("Skipping ", variantName, " because NULL or error")
    next
  }
  
  summary <- summary(usl.model)$coefficients
  print(summary)
  usl.result.tps[[ variantName ]] <- usl.model
  
  s <- scalability(usl.model)
  linear2 <- scalability(usl.model,0,0)
  
  maxX = max(variantBeanPlot$n) * 3

  p <- add_trace(p, x=ori$n, y=ori$ok, name=variantName) %>% #, name=t$hostname)
     # add_trace(p, x=bb$benchmark$n, y=bb$benchmark$failures) %>%
     add_lines(x = 0:maxX, y = s(0:maxX), name=paste0(variantName, " USL")) %>% 
     # add_lines(x = 0:maxX, y = linear(0:maxX), line = list(dash="dash"), name=paste0(variantName, " linear"))  %>% 
     add_lines(x = 0:maxX, y = linear2(0:maxX), line = list(dash="dash"), name=paste0(variantName, " linear"))
  maximum <- max(max(max(variantBeanPlot$ok), s(0:maxX))*1.1, maximum)
}

for (i in seq_along(usl.result.tps)) {
  name = names(usl.result.tps)[[i]]
  usl.model <- usl.result.tps[[i]]
  result = coef(usl.model)
  print(name)
  print(result)
  print(paste("peak.scalability ", peak.scalability(usl.model)))
  print(paste("scale.factor ", usl.model$scale.factor))
  NULL
}
saveRDS(usl.result.tps, paste0(resultDir, "/usl.result.rds"))

p %>% layout(yaxis = list(range = c(0, maximum))) 
```

```{r error=TRUE}
twopc <- data.table(
  N = c(1,3,6,9,12),
  X = c(250, 500, 790, 1000, 1250)
)

cdac <- data.table(
  N = c(1,3,6,9,12),
  X = c(250, 600, 1100, 1800, 2000)
)

lin <- data.table(
  N = c(1,3,6,9,12),
  X = c(250, 750, 6*250, 9*250, 12*250)
)


plot_ly(mode = 'trace') %>% 
  add_trace(twopc, x=twopc$N, y=twopc$X, name='2pc') %>% 
  add_trace(cdac, x=cdac$N, y=cdac$X, name='CDAC') %>% 
  add_trace(x=lin$N, y=lin$X, name='CDAClinear')
  
```

## Amdahl

```{r error=TRUE}
p <- plot_ly(type = 'scatter', mode = 'markers')  %>%
    layout(xaxis= list(title='Count'), yaxis = list(title = 'Throughput'))

maximum <- 0

amdahl.fit <- list()

# for(bb in variantBenchmarks) {
for(variantBeanPlot in variantBeans) {
  variantName = variantBeanPlot$variant[[1]]
  print(variantName)
  
  amdahl.model <- nls(ok ~ (lambda * n) / (1 + sigma * (n - 1)), variantBeanPlot, start=c(sigma=0.1, lambda=1000))
  
  print(summary(amdahl.model))
  
  sigma <- coef(amdahl.model)['sigma']
  lambda <- coef(amdahl.model)['lambda']
  
  amdahl.fit[[ variantName ]] <- amdahl.model
  
  g = function(n){ y = (lambda * n) / (1 + sigma * (n - 1)) }
  
  linear <- function(N) { N * lambda }
  
  maxX = max(bb$benchmark$n) * 2

  p <- add_trace(p, x=variantBeanPlot$n, y=variantBeanPlot$ok, name=bb$title) %>% #, name=t$hostname)
     # add_trace(p, x=bb$benchmark$n, y=bb$benchmark$failures) %>%
     add_lines(x = 0:maxX, y = g(0:maxX), linetype=paste0(bb$title, " Amdahl")) %>% 
     add_lines(x = 0:maxX, y = linear(0:maxX), line = list(dash="dash"), linetype=paste0(bb$title, " linear"))
  maximum <- max(max(max(bb$benchmark$throughput), g(0:maxX))*1.1, maximum)
}

saveRDS(amdahl.fit, paste0(resultDir, "/amdahl.fit.rds"))

p %>% layout(yaxis = list(range = c(0, maximum))) 
```

## Gustafson

\[\sigma + N(1-\sigma)\]

\[
X^{G}(N) = \lambda (\sigma + N(1-\sigma))
\]

```{r error=TRUE}

p <- plot_ly(type = 'scatter', mode = 'markers')  %>%
    layout(xaxis= list(title='Count'), yaxis = list(title = 'Throughput'))

maximum <- 0


for(bb in variantBenchmarks) {
  print(bb$title)
  
  gastafson.model <- nls(throughput ~ lambda * (sigma + n * (1 - sigma)), bb$benchmark, start=c(sigma=0.1, lambda=1000))
  

  # usl.model <- tryCatch({usl(throughput ~ nodeCount, bb$benchmark, method="nls")},
  #   error=function(e){cat("ERROR :",conditionMessage(e), "\n"); e})
  # 
  # if(inherits(usl.model, "error")) next
  # 
  print(summary(gastafson.model))
  
  sigma <- coef(gastafson.model)['sigma']
  lambda <- coef(gastafson.model)['lambda']
  
  g = function(n){ y = lambda * (sigma + n * (1 - sigma)) }
  
  linear <- function(N) { N * lambda }
  
  maxX = max(bb$benchmark$n) * 2

  p <- add_trace(p, x=bb$benchmark$n, y=bb$benchmark$throughput, name=bb$title) %>% #, name=t$hostname)
     # add_trace(p, x=bb$benchmark$n, y=bb$benchmark$failures) %>%
     add_lines(x = 0:maxX, y = g(0:maxX), linetype=paste0(bb$title, " Gustafson")) %>% 
     add_lines(x = 0:maxX, y = linear(0:maxX), line = list(dash="dash"), linetype=paste0(bb$title, " linear"))
  maximum <- max(max(max(bb$benchmark$throughput), g(0:maxX))*1.1, maximum)
}
p %>% layout(yaxis = list(range = c(0, maximum))) 

```

# Raw Data analysis

## disabled

<!--
```{r error=T}
variantBeanPlots <- lapply(variants, function(variant) {
  results <- lapply(variant$experiments, function(exp) {
    requests <- loadSimulationLogs(exp$experimentDir)
    n <- getN(nName, exp$testDescription)
    requests[,n:=n]
    # requests$nodeCount <- rep(nodeCount,nrow(requests)) 
    requests
    })
  
  # pirateplot(duration ~ request , data=requests, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)
  # print(results)
  combined <- rbindlist(results)
  combined[,variant:=variant$title]
  # combined$variant <- rep(variant$title,nrow(combined)) 
  combined
})

# print(variantBeanPlots)
for(variantBeanPlot in variantBeanPlots) {
  pirateplot(duration ~ n , data=variantBeanPlot, point.o = .01, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5,
             main = variantBeanPlot$variant[[1]])
}

pirateplot(duration ~ variant , data=rbindlist(variantBeanPlots), point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)

```
-->