---
output:
  html_document:
    fig_width: 15
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r set-options, echo=FALSE, cache=FALSE}
options(height = 10000, width = 100)
```

## Report
```{r echo=FALSE, message=FALSE}

source("ReportLib.R")

defaultFilePath <- "/Users/tim/workspace/account-modelling/ing-codegen-akka/results/Interesting/2018-12-04T16:13:16.183+01:00-2PCvsCDACClosedContention1000FindMaxAlt/1000CDAC/20568316-f7d7-11e8-be49-c49e6d304df4-com.ing.corebank.rebel.simple_transaction.closedsystem.rampup.AllToAllSimulation-u4000-m4.xlarge-n21-c42-p1"

option_list <- list(
  # make_option(c("-dir", "--from-directory"), action="store_true", default=FALSE,
    # help="Count the line numbers [default]"),
  make_option(c("-f", "--file"), default=defaultFilePath,
    help="File to process")
)

parser <- OptionParser(usage="%prog [options] file", option_list=option_list)

args <- parse_args(parser, positional_arguments = 0)
opt <- args$options
resultDir <- args$options$file
resultDir
# parse_args(parser, args = c("--help"))
# parse_args(parser, args = c("-f", "75"), positional_arguments = TRUE)
# parse_args(parser, args = c(), positional_arguments = TRUE)
```

<!-- ## Reading csv -->

```{r error=T}
experiment <- loadExperiment(resultDir)
```

```{r echo=FALSE}

print(toJSON(experiment$testDescription, pretty = T))

print(sprintf("Experiment start time: %s", experiment$performanceStartTime))
print(sprintf("Experiment end time: %s", experiment$performanceEndTime))

```

```{r}
gt <- gatlingTotals(experiment)
plot_ly(gt$allTotal, x=~time, y = ~count, name = 'all count', type = 'scatter', mode = 'lines', fill = 'tozeroy') %>%
  # add_trace(y = ~all$count, name = 'all2 count') %>%
  add_trace(y = ~ko, name = 'ko count') %>%
  add_trace(y = ~ok, name = 'ok count') %>%
  layout(title='Requests over time', yaxis = list(title = 'Request count'), xaxis= list(title='Time'))
```

## Responses per step

```{r error=T}
plot_ly(getBestStep(experiment)$data, split=~status, x=~time, y=~count, mode = 'markers', type='scatter')
```

```{r}
pirateplot(count ~ status , data=experiment$gatling, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0)
```

```{r}
pirateplot(count ~ request , data=experiment$gatling, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0)
```

```{r}
pirateplot(count ~ host , data=experiment$gatling, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0)
```

```{r}
pirateplot(percentiles99 ~ status , data=experiment$gatling, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0)
```

## Users/connections over time
```{r}
# users
plot_ly(gt$users, x=~time, y=~active, name = 'all count', type = 'scatter', mode = 'lines', fill = 'tozeroy')
```

<!-- ## Graph per metric per hostname -->
<!-- ```{r} -->
<!-- kt <- data.table(kamonTimers) -->

<!-- showMetric <- function(entty, metri){ -->
<!--   cpu <- kt[entity==entty] -->

<!--   cpuPerHost <- split(cpu, cpu$hostname) -->
<!--     # remove last because it is somehow always "hostname" -->
<!--   cpuPerHost <- cpuPerHost[1:length(cpuPerHost)-1] -->
<!--   # print(cpuPerHost) -->

<!--   ps <- lapply(cpuPerHost, function(cp) { -->
<!--     metrics <- cp[metric==metri] -->
<!--     plot_ly(metrics, x=~time, y = ~mean, type = 'scatter', mode = 'lines', name = sprintf('mean %s', metri), fill = 'tozeroy') %>% -->
<!--     add_trace(y = ~cp[metric=="cpu-system"]$mean, name = 'mean cpu-system') %>%  -->
<!--     layout(  -->
<!--       # shapes=list(type='line', x0= 1, x1= 1, line=list(dash='dot', width=1)), -->
<!--       yaxis = list( -->
<!--          ticksuffix = '%', -->
<!--          domain = c(0,1.0) -->
<!--         ) -->
<!--       ) -->
<!--   }) -->

<!--   # print(cpuPerHost) -->
<!--   # print(length(cpuPerHost)) -->

<!--   p <- subplot(ps, nrows = length(cpuPerHost), shareX = TRUE)  -->
<!--   # %>%  -->
<!--   #   layout(  -->
<!--   #     yaxis = list( -->
<!--   #       title = "", -->
<!--   # zeroline = FALSE, -->
<!--   # showline = FALSE, -->
<!--   # showticklabels = FALSE, -->
<!--   # showgrid = FALSE -->
<!--   #     )  -->
<!--   #   ) -->
<!--   #  -->
<!--   p -->
<!-- } -->

<!-- showMetric("cpu", "cpu-user") -->

<!--  # showMetric("memory", "memory-used") -->

<!-- # kt[entity=="memory"] -->
<!-- # # showMetric("memory", "memory-used") -->
<!-- mem <- kt[entity=="memory"] -->
<!-- memPerHost <- split(mem, mem$hostname) -->
<!-- memPerHost <- memPerHost[1:length(memPerHost)-1] -->
<!-- #  -->
<!-- ps <- lapply(memPerHost, function(c) { -->
<!--   plot_ly(c[metric=="memory-used"], x=~time, y = ~mean, type = 'scatter', mode = 'lines', name = sprintf('mean %s', "memory-used"), fill = 'tozeroy') %>% -->
<!--   # add_trace(y = ~c[metric=="cpu-system"]$mean, name = 'mean cpu-system') %>% -->
<!--   layout( -->
<!--     yaxis = list( -->
<!--        # ticksuffix = '%' -->
<!--       ) -->
<!--     ) -->
<!-- }) -->

<!-- subplot(ps, nrows = length(memPerHost), shareX = TRUE) -->

<!-- ``` -->

## Graph per metric, hostname

```{r error=T}
# kt

# print(levels(cpu$entity))

showMetric <- function(dataName, metri, ymax, selector="mode", value="max", split="none"){
  metrics <- getMetricsData(experiment, dataName, F)[get(selector) == metri,]
     # experiment$kamonTimers[metric == metri] 
  
  p <- metrics %>%
    plot_ly(mode = 'lines+markers', type='scatter') %>% 
    group_by(host) %>% 
    layout(xaxis= list(title='Time'), yaxis = list(title = metri)) %>% hide_legend()
  
    p <- if(split != "none") {
      p %>% add_trace(split = ~get(split), name = paste0(metrics$host, get(split, metrics)), x = ~time, y = ~get(value), text=paste0(metrics$host, get(split, metrics)))
    } else {
       p %>% add_trace(name = ~host, x = ~time, y = ~get(value), text=~host)
    }
    # p <- if("segment" %in% colnames(metrics)){
    #     p %>% add_trace(split = ~segment, name = ~host, x = ~time, y = ~get(value), text=~host)
    # } else {
    #     p %>% add_trace(name = ~host, x = ~time, y = ~get(value), text=~host)
    # }
  p
}

metrics <- list(
  showMetric("host.cpu", "combined", 100, "mode"),
  # showMetric("cpu-user", 100),
  # showMetric("cpu-system", 100),
  showMetric("jvm.memory", "used", 1500000000, "measure", "max", "segment"),
  showMetric("akka.http.server.active-requests", "akka.http.server.active-requests", 100, "name"),
  # showMetric("mailbox-size")
  showMetric("akka.http.server.open-connections", "akka.http.server.open-connections", 100, "name")
  # showMetric("connection-open")
)

subplot(metrics, nrows = length(metrics), shareX = TRUE, titleY = TRUE)  #%>%
    # layout(legend = list(xanchor="center",yanchor="top",x = -0.3, y = -0.3))
```

# ```{r error=T}
# metrics <- levels(experiment$kamonTimers$metric)
# 
# multiMetrics <- function(metrics) {
# graphs <- lapply(metrics, function(metric) {
#     showMetric(metric) %>% layout(annotations = list(
#       text = metric,
#       xref = "paper",
#       yref = "paper",
#       yanchor = "bottom",
#       xanchor = "center",
#       align = "center",
#       x = 0.5,
#       y = 1,
#       showarrow = FALSE
#     ))
# })
# 
# 
# subplot(graphs, nrows = as.integer(length(graphs) / 2), shareX = TRUE)
# }
# 
# multiMetrics(metrics[1:10])
# multiMetrics(metrics[11:20])
# multiMetrics(metrics[21:30])
# multiMetrics(metrics[31:40])
# multiMetrics(metrics[41:50])
# multiMetrics(metrics[51:60])
# multiMetrics(metrics[61:70])
# multiMetrics(metrics[71:75])
# ```


## Kamon stats

### Span processing time

```{r error=T}

spans <- getMetricsData(experiment, "span.processing-time")

spans$`p99.9` <- nanoseconds(spans$`p99.9`)$second
spans$`p99.0` <- nanoseconds(spans$`p99.0`)$second
spans$`p95.0` <- nanoseconds(spans$`p95.0`)$second
spans$`p90.0` <- nanoseconds(spans$`p90.0`)$second
spans$`p70.0` <- nanoseconds(spans$`p70.0`)$second
spans$`p50.0` <- nanoseconds(spans$`p50.0`)$second

head(spans)
# head(experiment$kamonTimers[category == "trace-segment",])
# 
spans %>%
  plot_ly(mode = 'lines+markers', type='scatter') %>%
  group_by(host, parentOperation) %>%
  
  # group_by() %>%
  # add_trace(split = ~entity, name = ~trace, x = ~time, y = ~`p99.9`, text=~host)
  add_trace(split = ~operation, x = ~time, y = ~`p99.9`, text = paste('host: ', spans$host, 
                              '\n p99.9: ', spans$`p99.9`,
                              '\n p99: ', spans$`p99.0`,
                              '\n p95: ', spans$`p95.0`,
                              '\n p90, ', spans$`p90.0`,
                              '\n p70, ', spans$`p70.0`,
                              '\n p50: ', spans$`p50.0`
                              ), name=paste0(spans$parentOperation, spans$operation))

```

### Span split per host

```{r error=T, fig.show='hold'}

# spans <- getMetricsData(experiment, "span.processing-time")
# 
# spans$`p99.9` <- nanoseconds(spans$`p99.9`)$second
# spans$`p99.0` <- nanoseconds(spans$`p99.0`)$second
# spans$`p95.0` <- nanoseconds(spans$`p95.0`)$second
# spans$`p90.0` <- nanoseconds(spans$`p90.0`)$second
# spans$`p70.0` <- nanoseconds(spans$`p70.0`)$second
# spans$`p50.0` <- nanoseconds(spans$`p50.0`)$second

# head(spans)
# head(experiment$kamonTimers[category == "trace-segment",])
# 

l <- levels(droplevels(spans$operation))

m <- lapply(l, function(o) {
# for(o in l) {

  opera <- spans[operation == o,]
  
  p <- opera %>%
  plot_ly(type = 'scatter', mode = 'lines') %>% 
           layout(title = o) %>%
  group_by(host, parentOperation) %>%
  
  # group_by() %>%
  # add_trace(split = ~entity, name = ~trace, x = ~time, y = ~`p99.9`, text=~host)
  add_trace(x = ~time, y = ~`p99.9`, text = ~host, name=paste0('p99.9', opera$parentOperation)) %>%
  add_trace(x = ~time, y = ~`p99.0`, text = ~host, name=paste0('p99.0', opera$parentOperation)) %>%
  add_trace(x = ~time, y = ~`p95.0`, text = ~host, name=paste0('p95.0', opera$parentOperation)) %>%
  add_trace(x = ~time, y = ~`p90.0`, text = ~host, name=paste0('p90.0', opera$parentOperation)) %>%
  add_trace(x = ~time, y = ~`p70.0`, text = ~host, name=paste0('p70.0', opera$parentOperation)) %>%
  add_trace(x = ~time, y = ~`p50.0`, text = ~host, name=paste0('p50.0', opera$parentOperation))
            # paste('host: ', spans$host, 
            #                   '\n p99.9: ', spans$`p99.9`,
            #                   '\n p99: ', spans$`p99.0`,
            #                   '\n p95: ', spans$`p95.0`,
            #                   '\n p90, ', spans$`p90.0`,
            #                   '\n p70, ', spans$`p70.0`,
            #                   '\n p50: ', spans$`p50.0`
            #                   )
  # print(p)
# }
})

print(as.list(m))
 
subplot(m, nrows = length(m), shareX = TRUE, titleY = TRUE)

```

## C* Metrics

```{r error=T}
ay <- list(
  # tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  range = c(0,1)
)


# todo should be without `compute.internal.jvm.`
experiment$db %>%
  plot_ly(mode = 'lines+markers', type='scatter') %>%
  group_by(host) %>%
  # group_by(trace) %>%
  add_trace(x = ~time, y = ~os.systemCpuLoad, name='systemCpuLoad', yaxis = "y2") %>%
  add_trace(x = ~time, y = ~os.processCpuLoad, name='processCpuLoad', yaxis = "y2") %>%
  add_trace(x = ~time, y = ~heapMemoryUsage.used, name='heapMemoryUsage.used') %>%
  add_trace(x = ~time, y = ~loadedClasses, name='loadedClasses') %>%
  add_trace(x = ~time, y = ~nonHeapMemoryUsage.used, name='nonHeapMemoryUsage.used') %>%
  add_trace(x = ~time, y = ~os.systemLoadAverage, name='os.systemLoadAverage') %>%
  layout(
    yaxis2 = ay
    # xaxis = list(title="tim")
  )
```

### Clashes vs ko's
```{r error=T}

commits <- tryCatch(getMetricsData(experiment, "TransactionManager.Commit", F), error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})
retries <- tryCatch(getMetricsData(experiment, "2pc.retries", F), error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})
timeouts <- tryCatch(getMetricsData(experiment, "2pc.timeouts", F), error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})


ay <- list(
  # tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  range = c(0,100)
)

 nodeCpu <- getMetricsData(experiment, "host.cpu", F)[mode == "combined"] %>% group_by(host)

# experiment$kamonTimers
# experiment$kamonTimers[category == "trace-segment",]
# nodeCpu <- experiment$kamonTimers[metric=='cpu-idle'] %>% group_by(hostname)
# nodeCpu$meanCpuSum <- 1-(nodeCpu$mean / 100)
# nodeCpu

# plot_ly(nodeCpu, x = ~time) %>%

  # add_lines(y=~meanCpuSum)

clashes <- NULL
try(
  clashes <- getMetricsData(experiment, "lockClash", F)
)

p <- plot_ly(type = 'scatter', mode='lines+markers') %>%
  add_lines(x = gt$allTotal$time, y = gt$allTotal$ko, name='ko') %>%
  add_lines(x = gt$allTotal$time, y = gt$allTotal$ok, name='ok') %>%
  add_trace(data=commits %>% group_by(host), x=~time, y=~count, text=~host, symbol=~host, mode='markers', color='2PC-M-Commits') %>%
  add_lines(data=experiment$db %>% group_by(host), x=~time, y = ~os.processCpuLoad * 100, name='DB-cpu', yaxis = "y2", text=~host) %>%
  add_lines(data=nodeCpu, x=~time, y=~max, name='node-cpu', yaxis = "y2", text=~host)
if(!is.null(retries)) {
  p <- add_trace(p, data=retries %>% group_by(host), x=~time, y = ~count, name='2pc-retries', text=~host, mode='markers', symbol=~host, color='2pc-retries')
}
if(!is.null(timeouts)) {
  p <- add_trace(p, data=timeouts %>% group_by(host), x=~time, y = ~count, text='2pc-timouts', mode='markers', symbol=~host, color='2pc-timeouts')
}
if(!is.null(clashes)){
  p <-  add_trace(p, data=clashes %>% group_by(host), x=~time, y = ~count, text='lockClash', mode='markers', symbol=~host, color='lockClash')
}

p %>% layout(
  yaxis2 = ay
  # xaxis = list(title="time")
)
```

### Message throughput

```{r error=T}

messages <- tryCatch(getMetricsData(experiment, "akka.system.processed-messages", F), error=function(e){cat("ERROR :",conditionMessage(e), "\n"); NULL})
messages <- messages[,list(count = sum(count)), by = list(host, time)]
plot_ly(messages %>% group_by(host), x=~time, y=~count, type = 'scatter', mode='lines+markers', symbol=~host)

```


### Responses per host

Http load is divided equally over all hosts, therefor all hosts should perform similarly.

```{r error=T}

httpCounters <- getMetricsData(experiment, "host.cpu", F)[mode == "combined"] # experiment$kamonCounters[category=="http-server" & metric %like% '-',]

httpCounters %>%
  plot_ly(mode = 'lines+markers', type='scatter') %>%
  group_by(host) %>%
  add_trace(split = ~host, name = ~host, x = ~time, y = ~p99.9, text=~host)

# op <- par(no.readonly = TRUE)
# for(m in levels(droplevels(httpCounters$metric))) {
#   # print(m)
#   data <- httpCounters[metric == m,]
#   pirateplot(value ~ host , data, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, main=m, xaxt="n")
#   # print(data)
#   hostnames <- levels(droplevels(data$host))
#   # print(hostnames)
#   axis(1, labels=host, at=1:length(host), las = 2)
# }
# 
# par(op)
```

### Network metrics per host

```{r error=T}
m <- list(
  showMetric("host.network.bytes", "received", 10000, "direction", "count"),
  showMetric("host.network.bytes", "transmitted", 10000, "direction", "count"),
  showMetric("host.network.packets", "received", 10000, "direction", "count", "state"),
  showMetric("host.network.packets", "transmitted", 10000, "direction", "count", "state")
)

subplot(m, nrows = length(m), shareX = TRUE, titleY = TRUE)
```

### 2PC per host

```{r error=T}
m <- list(
  showMetric("create-TransactionManager", "create-TransactionManager", 10000, "name", "count"),
  showMetric("create-TransactionParticipant", "create-TransactionParticipant", 10000, "name", "count"),
  showMetric("akka.system.active-actors", "akka.system.active-actors", 10000, "name", "max")
)

subplot(m, nrows = length(m), shareX = TRUE, titleY = TRUE)
```

### Mem per host

```{r error=T}
m <- list(
  showMetric("host.memory", "used", 10000, "mode", "p99.0"),
  showMetric("host.memory", "cached-and-buffered", 10000, "mode", "p99.0")
)

subplot(m, nrows = length(m), shareX = TRUE, titleY = TRUE)
```


### JVM per host

```{r error=T}

plot_ly(getMetricsData(experiment, "jvm.class-loading", F) %>% group_by(host), x=~time, y=~value, split=~mode, mode = 'lines+markers', type='scatter')
```
```{r error=T}
m <- list(
  showMetric("jvm.gc", "jvm.gc", 10000, "name", "p99.0"),
  showMetric("jvm.gc.promotion", "jvm.gc.promotion", 10000, "name", "p99.0", "space"),
  showMetric("jvm.hiccup", "jvm.hiccup", 10000, "name", "p99.0")
)

subplot(m, nrows = length(m), shareX = TRUE, titleY = TRUE)
```
```{r error=T}
plot_ly(getMetricsData(experiment, "jvm.memory.buffer-pool.usage", F) %>% group_by(host), x=~time, y=~value, split=~pool, mode = 'lines+markers', type='scatter', text=~host)
```

#### Threads

```{r error=T}
plot_ly(getMetricsData(experiment, "jvm.threads", F) %>% group_by(host), x=~time, y=~value, split=~measure, mode = 'lines+markers', type='scatter', text=~host)
```

### Shard id calls

#### Accounts
```{r error=T}
try({
shards <- getMetricsData(experiment, "shardid-Account", F)

list(
plot_ly(shards %>% group_by(host), x=~time, y=~count, split=~shardId, mode = 'lines+markers', type='scatter', text=~host),

plot_ly(shards %>% group_by(msgType, shardId), x = ~host, y = ~count, split=~shardId, type = 'bar') %>%
  # add_trace(y = ~LA_Zoo, name = 'LA Zoo') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'group')
)
})

```

#### 2PC Managers
```{r error=T}
try({
shards <- getMetricsData(experiment, "shardid-2pc", F)

#   all[ok, ok:=i.count, on = c(time="time")]
# messages <- messages[,list(count = sum(count)), by = list(host, time)]

filtered <- shards[,list(count=sum(count)),by=list(shardId,msgType, host)]

list(
# plot_ly(shards %>% group_by(host), x=~time, y=~count, split=~shardId, mode = 'lines+markers', type='scatter', text=~msgType),

plot_ly(shards[,list(count=sum(count)),by=list(shardId, host)] , x = ~shardId, y = ~count, split=~host, type = 'bar') %>%
   layout(title="Total number of messages per shardId, by host"),
plot_ly(shards[,list(count=sum(count)),by=list(msgType, host, shardId)] , x = ~shardId, y = ~count, split=~host, type = 'bar') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack', title="Total number of messages per shardId, sum per host"),
plot_ly(shards[,list(count=sum(count)),by=list(shardId,msgType, host)] , x = ~shardId, y = ~count, split=~msgType, type = 'bar') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack', title="Total number of messages per shardId, by msgType"),
plot_ly(filtered, x =~shardId, y = ~count, split=~msgType, type = 'bar', color = ~host) %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack', title="Total number of messages per shardId, by msgType and host")
)
})

```

# Mean response time per application host

# ```{r error=T}
# http <- experiment$kamonTimers[category=='trace' & entity %like% '-'] 
# 
# 
# 
# # as.duration(http$upper)
# 
# http %>%
#   plot_ly(mode = 'lines+markers', type='scatter') %>%
#   group_by(hostname) %>%
#   add_trace(split = ~hostname, name = ~entity, x = ~time, y = ~mean)
# 
# #pirateplot(count ~ host , data=experiment$gatling, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0)
# op <- par(no.readonly = TRUE)
# pirateplot(mean ~ hostname , http[time >= experiment$performanceStartTime & time <= experiment$performanceEndTime,], quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, xaxt="n")
# axis(1, labels=levels(http$hostname), at=1:length(levels(http$hostname)), las = 2)
# par(op)
# ```

## Total RPS vs OK
```{r error=T}
percentOk <- gt$all$ok / gt$all$count

plot_ly(gt$all, x=~count, y=~percentOk, type='scatter', mode="markers",color = ~-percentiles99, colors="RdYlGn") %>%
  layout(title='RPS vs OK', yaxis = list(title = 'Percentage OK'), xaxis= list(title='RPS'))

plot_ly(gt$all, x=~count, y=~percentOk, type='scatter', mode="markers",color = ~-percentiles99, colors="RdYlGn") %>%
  layout(title='RPS vs OK', yaxis = list(title = 'Percentage OK'), xaxis= list(title='RPS'))

```

## RPS vs max response time
```{r error=T}
# color = ~-percentiles99, colors="RdYlGn",
plot_ly(gt$all, x=~ok, y=~`percentiles99-9`, type='scatter', mode="markers", name="OK") %>%
  add_trace(x=~ko, y=~`percentiles99-9`, type='scatter', mode="markers", name="KO")

```

## Compare percentiles

```{r error=T}
plot_ly(gt$all, type = 'scatter', mode = 'lines', fill = 'tozeroy') %>%
  # add_trace(y = ~all$count, name = 'all2 count') %>%
  add_trace(y = ~percentiles50, name = 'p50') %>%
  add_trace(y = ~percentiles95, name = 'p95') %>%
  add_trace(y = ~percentiles99, name = 'p99') %>%
    add_trace(y = ~`percentiles99-9`, name = 'p99.9') %>%
      # add_trace(y = ~count, name = 'count', yaxis = "y2") %>%
  layout(yaxis = list(title = 'Percentiles'), xaxis= list(title='Time'))
```

```{r error=T}
plot_ly(gt$all, type = 'scatter', mode = 'markers') %>%
  # add_trace(y = ~all$count, name = 'all2 count') %>%
  add_trace(x=~ok, y = ~percentiles50, name = 'p50') %>%
  add_trace(x=~ok, y = ~percentiles95, name = 'p95') %>%
  add_trace(x=~ok, y = ~percentiles99, name = 'p99') %>%
    add_trace(x=~ok, y = ~`percentiles99-9`, name = 'p99.9') %>%
      # add_trace(y = ~count, name = 'count', yaxis = "y2") %>%
  layout(yaxis = list(title = 'Percentiles'), xaxis= list(title='OK count'))
```

## Total OKs over time
```{r error=T}


p <- plot_ly(gt$all, x = ~time, y = ~ok)

p
```


## BoxPlot percentiles

# ```{r error=T}
# 
# plot_ly(type = 'box', boxpoints = 'all') %>%
#   add_boxplot(y = gt$all$percentiles95, name="p95") %>%
#   add_boxplot(y = gt$all$percentiles99, name="p99") %>%
#   add_boxplot(y = gt$all$`percentiles99-9`, name="p99.9") %>%
#   add_boxplot(y = gt$all$`percentiles99-99`, name="p99.99")
# 
# ```

## Raw Gatling simulation.log

```{r error=TRUE}
requests <- loadSimulationLogs(resultDir)

oks <- requests[status=="OK",]
```

```{r error=T}

# plot_ly() %>% 
plot_ly(requests, mode = 'markers', type='scattergl', opacity=0.2) %>%
  add_trace(split = ~hostname, x=~end, y=~duration, text=~hostname, name="duration") # %>%
  # plot_ly(x=~end, y=~duration, mode = 'markers', type='scattergl', name="duration")

# slow loading
# plot_ly(type = 'box', boxpoints = 'all' ) %>%
  # add_boxplot(y = requests$duration, name="duration") 
```

<!-- not nice visualisation
````{r error=TRUE}

library(beanplot)

beanplot(requests$duration, what=c(1,1,1,0), log="", col = c("#CAB2D6", "#33A02C", "#B2DF8A"), border = "#CAB2D6")

```
-->

### Latency vs Throughput, already done see RPS vs latency

# ```{r error=TRUE}
# steps <- getBestStep(experiment)$allSteps
# 
# gt$all
# 
# p <- plot_ly(mode = 'markers', type='scatter')
# 
# for(step in steps) {
#   p <- add_trace(p, data=step[status=="ok", ], x=~count, y=~`percentiles99-9`, name=~count)
# }
# 
# p
# ```

````{r error=TRUE}

# pirateplot(duration ~ request , data=oks, point.o = .005, quant = c(.01, .99))
ggplot(oks, aes(x = request, y = duration)) +
  geom_pirate(aes(colour = request, fill = request, group=start), points_params = list(alpha = .01), lines_params = list(size = 0.2, alpha = 0.1),
              violins_params = list(scale = "width"),
              show.legend = TRUE) +
  theme(legend.position="bottom") + labs(color='variant') + ggtitle("Latency vs Throughput")



```

```{r error=TRUE}

# pirateplot(duration ~ request , data=requests, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)

pirateplot(duration ~ request , data=oks, point.o = .005, quant = c(.01, .99),  avg.line.fun = median, inf.f.o = 0, inf.b.o = 0, jitter.val=.2, point.cex=0.5)

```

```{r error=TRUE}
# m <- as.matrix(ok$min)

# m <- with(ok, table(time, percentiles99))  

# m

# ay <- list(
#   # tickfont = list(color = "red"),
#   overlaying = "y",
#   side = "right"
#   # title = "second y axis"
# )

plot_ly(gt$ok, x=~time, y=~percentiles99, name="ok", type = 'scatter') %>%
  add_trace(y = ~gt$ko$percentiles99, name = 'ko')
  # add_trace(y = ~trace_2, name = 'trace 2', mode = 'markers')
# %>% add_surface()
```
